---
title: "CSC8631Report"
author: "Yang Cong"
date: "2021/11/23"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

```{r ProjectTemplate, include=FALSE}
library(ProjectTemplate)
load.project()
```



# 1. Analyse the gender, age range and country of learners
### Firstly, we would like to get an overall picture of the gender and age distribution of the learners in order to get a general idea of the profile of our subjects.
## Analyse the gender
### When making statistical distinctions by gender, we first eliminate all Unknown values. Using codes:
```{r analysis the gender, echo=TRUE}
enr_gender = filter(enrolments, gender == "male" | gender == "female" )
```
### And then we can  easily draw the bar charts. From the plot we can see that there are more male learners than female.
```{r echo=FALSE}
g_enr_gender = ggplot(data = enr_gender)
g_enr_gender_bar = g_enr_gender + geom_bar(aes(x = gender, fill = gender ),  width = 0.4) +
                   theme(panel.grid.major =element_blank(),  # remove the borders
                   panel.grid.minor = element_blank(),
                   panel.background = element_blank(),
                   axis.title =  element_text(size=12,face = "bold"),
                   axis.text.x =   element_text(hjust = 1, # Adjusting the position of text in horizontal coordinates
                                                size=15), # Adjusting the font size of text in horizontal coordinates
                                                plot.margin=unit(rep(3,4),'lines'))     # Set image margins 
g_enr_gender_bar
```

## Analyse the age range
### Same as analyse the gender, we should firstly remove the Unknown data.
```{r analysis the age, echo=FALSE}
#enrolments
enr_age = filter(enrolments, age_range != "Unknown")
#enr_age
#Find out what the age ranges are
index = duplicated(enr_age$age_range)
enr_age_list = enr_age[!index,9]
```
### And to reduce the amount of arithmetic, I first simplified the data frame by extracting only the useful data. This operation will be used frequently later in the data analysis and is useful for improving the performance of the analysis.
```{r echo=TRUE}
enr_age = select(enr_age, learner_id, age_range)
```
### The graph shows that the age distribution of the learners is very wide, but most of the students are already adults. We can therefore assume that they are more mentally mature.
```{r echo=FALSE}
age_num = c()
for(i in 1:7){
  #generating single country data frame
  single_age = filter(enr_age,age_range == as.character(enr_age_list[i,1]))
  #compute the number of people that age
  nums = dim(single_age)[1]
  #Add this num to the list
  age_num = c(age_num ,nums)
}
age_num = as.data.frame(age_num)
enr_age_num = cbind(enr_age_list,age_num)
#enr_age_num
ggplot(data=enr_age_num, aes(x=age_range, y=age_num)) + geom_point(color="red") + xlab("Age_range")
```

## Analyse the country
### It is interesting to analyse the nationality of the learners, we can derive their learning habits from their nationality, which is related to the culture of their country.
```{r include=FALSE}
#analysis the country
enr_country = filter(enrolments, country != "Unknown" )
#enr_country
#Find out what the countries are
index = duplicated(enr_country$country)
enr_country_list = enr_country[!index,8]    
#enr_country_list
#educed data volume and accelerated computing
enr_country = select(enr_country,country)
country_num = c()
for(i in 1:153){
  #generating single country data frame
  single_country = filter(enr_country,country == as.character(enr_country_list[i,1]))
  #compute the number of people that country
  nums = dim(single_country)[1]
  #Add the uncomplete rate for this step to the list
  country_num = c(country_num ,nums)
}
country_num 
#Transformation into a data framework
country_num = as.data.frame(country_num)
#combine
enr_country_num = cbind(enr_country_list,country_num)
```
### In fact there are so many countries that it is difficult for us to show them all in one map. We have therefore eliminated the countries with a small number of learners so that we can easily focus on the more valuable objects of analysis.
```{r}
enr_country_num = filter(enr_country_num, country_num>10)
```
### If I used a simple bar chart, some of the countries would stand out too much and detract from the overall graph, so I have chosen to use a fan chart. To give a more visual representation of the number of learners in each country, I have also calculated the percentage of learners and labelled it on the graph.
### The graph shows that most of the students are from the UK, India and Nigeria. And as non-native English learners make up a large group, I think schools should provide them with some language assistance.
```{r echo=FALSE}
enr_country_num = arrange(enr_country_num,desc(country_num))

myLabel = as.vector(enr_country_num$country)   ## Conversion to vectors, otherwise the labels of the legend may not match the actual order
myLabel = paste(myLabel, "(", round(enr_country_num$country_num / sum(enr_country_num$country_num) * 100, 2), "%) ", sep = "")   ## Use round() to retain two decimal places for the result

ggplot(enr_country_num, aes(x = "", y=country_num, fill = country)) + geom_bar(stat = "identity") +
          coord_polar(theta = "y") + 
          labs(x = "", y = "", title = "") + theme(axis.ticks = element_blank()) + 
          theme(legend.title = element_blank(), legend.position = "top") + 
          scale_fill_discrete(breaks = enr_country_num$country, labels = myLabel)   ## Replace the original legend label with the current myLabel
```


# 2. Analyse the leaving survey response
### In this step I tried to analyse what stage the learners were at when they left the study.As you can see from the graph most people managed to complete all the steps after several attempts, but there were some who gave up just as soon as they started trying, I think the mindset of this group needs to be adjusted, their patience is too low.
### At the same time there is another group of people who, despite many attempts, are still at a more rudimentary stage and I think this group needs some technical guidance from the school.
```{r echo=FALSE}
#analysis the leaving
ggplot(data=leaving_survey_responses,
       aes(x=last_completed_step_number, y=last_completed_step)) +geom_point(stat = "sum", color="darkred")+
       theme(
          axis.title =  element_text(size=12,face = "bold"),
          axis.text.x =   element_text(hjust = 1, # Adjusting the position of text in horizontal coordinates
                                       size=15),  # Adjusting the font size of text in horizontal coordinates
          plot.margin=unit(rep(3,4),'lines'))     # Set image margins  
```


# 3. Analyse the false rate
### In this step I counted the error rate of each question and showed the ones with the highest error rate. I believe that the teaching methods for the knowledge points covered in these questions need to be improved.
```{r echo=FALSE}
#Find out what the problems are
index = duplicated(question_response$quiz_question)
question_response_quiz = question_response[!index,2]

#compute the false rate for each question
false_rate = data.frame()
for(i in 1:29){
  #generating single question's data frame
  question_response_false = filter(question_response,quiz_question == as.character(question_response_quiz[i,1]))
  #compute the num of true answers
  true_answers = select(question_response_false,correct)
  e = unlist(true_answers)
  true_times = sum(e == "false")
  #compute the rate
  question_response_false = mutate(question_response_false,quiz_false_rates =     true_times/dim(question_response_false)[1])
  #add the rate to the data frame
  false_rate = rbind(false_rate,question_response_false) 
}
#false_rate
#view(false_rate)
#analysis the false rate of each quiz
#quiz data de-duplication
index = duplicated(false_rate$quiz_question)
quiz_rate = false_rate[!index,]
quiz_rate_plot = select(quiz_rate,quiz_question, quiz_false_rates)
#quiz_rate_plot
ggplot(data = quiz_rate_plot, aes(x = quiz_question, y = quiz_false_rates, fill= quiz_question)) + geom_bar(stat='identity') + 
              theme(panel.grid.major =element_blank(),  #  remove the borders
                    panel.grid.minor = element_blank(),
                    panel.background = element_blank(),
                    axis.title =  element_text(size=12,face = "bold"),
                    axis.text.x = element_text(size = 0),  # Adjusting the font size of text in horizontal
                    plot.margin=unit(rep(3,4),'lines'))     # Set image margins 
```


# 3. Analyse the activity step
### In this section we look at the unfinished rate of the activity. I have counted the failure rates for each step of the campaign and listed the six steps with the highest failure rates. I think the design of these six steps may need to be improved.
```{r echo=FALSE}
#analysis the activity step
#Find out what the activities are
index = duplicated(step_activity$step)
step_activity_step = step_activity[!index,2]    
#step_activity_step
step_activity2 = select(step_activity, step, last_completed_at)
#compute the complete rate
uncomplete_rate = c()
for(i in 1:58){
  #generating single step's data frame
  step_activity_step_single = filter(step_activity2,step == as.character(step_activity_step[i,1]))
  #compute the times that did not finish
  times = select(step_activity_step_single,last_completed_at)
  e = unlist(times)
  uncomplete_times = sum(e == "")
  #Add the uncompleted rate for this step to the list
  uncomplete_rate = c(uncomplete_rate,uncomplete_times/dim(step_activity_step_single)[1])
}
#Transformation into a data framework
uncomplete_rate = as.data.frame(uncomplete_rate)
#combine
step_activity_step = cbind(step_activity_step,uncomplete_rate)
#step_activity_step
#Removal of lower values
step_activity_step = filter(step_activity_step, uncomplete_rate > 0.15)
ggplot(data = step_activity_step, aes(x = as.factor(step), y = uncomplete_rate, fill= step)) + geom_bar(stat='identity') + 
  theme(panel.grid.major =element_blank(),  
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.title =  element_text(size=12,face = "bold"),
        axis.text.x = element_text(size = 12),  
        plot.margin=unit(rep(3,4),'lines'))     

```